Designing Imaging Surveys for a Retrospective Relative Photometric Calibration

### 2012-09-27 paper/self_calibration_I.tex
remove large-scale from paper title

\shorttitle{Designing Large-Scale Imaging Surveys for Retrospective Relative Photometric Calibration}
\shortauthors{Holmes et al.}

@@

\title{Designing Large-Scale Imaging Surveys for a Retrospective Relative Photometric Calibration}

>>>>

\shorttitle{Designing Imaging Surveys for Retrospective Relative Photometric Calibration}
\shortauthors{Holmes et al.}

@@

\title{Designing Imaging Surveys for a Retrospective Relative Photometric Calibration}
